---
title: "Ongoing Changes in the AusE Amplifier System"
author: "Martin Schweinberger"
date: "12 November 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Habilitation (in progress)
*Acquisition, Variation, and Diachronic Change in and across English Amplifiier Systems*

- yeah... just it would make it *so awkward* eh you know (ICE-NZ S1A-001:1\$M)

- um... sara's got a *really nice* sleeveless green... you know coat jacket (ICE-NZ S1A-002:1\$Q)

- she was a *very nervous* sort of a woman (ICE-NZ S1A-018:1\$A)

## Intensification

Intensification is related to the semantic category of *degree* (degree adverbs) and ranges between very low intensity (downtoning) and very high (amplifiers) \textcolor{gray}{\citep[589--590]{quirk1985comprehensive}.}
\begin{itemize}
\item Amplifiers \textcolor{gray}{\citep{tagliamonte2008intensifiers}}
\begin{itemize}
\item Maximizers (e.g. \textit{completely})
\item Boosters (e.g. \textit{very much})
\end{itemize}
\item \textcolor{gray}{Downtoners}
\begin{itemize}
\item \textcolor{gray}{Approximators (e.g. \textit{almost})}
\item \textcolor{gray}{Compromisers (e.g. \textit{more or less})}
\item \textcolor{gray}{Diminishers (e.g. \textit{partly})}
\item \textcolor{gray}{Minimizers (e.g. \textit{hardly})}

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

